\thetitle

### 2008-05-28 paper.tex
More tweaking of sizes, figures and breaks.

\begin{table*}
\begin{center}
\small
\begin{tabular}{|c|c|l|}
\multicolumn{1}{c}{\textbf{model}} &
\multicolumn{1}{c}{\textbf{transformation}} &
\multicolumn{1}{c}{\textbf{description}} \\
\hline
{\footnotesize{GMM}} & --- & the general matrix model \\\hline\hline
time uniform & $A'=A(\ones{d_t \times d_t}/d_t)$ & all start times are equally likely \\\hline
node uniform & $S'=S(\ones{n \times n}/n)$~~~~$D'=D(\ones{n \times n}/n)$ & nodes behave stochastically identically with respect to flows \\\hline
full uniform & \textit{all uniform transformations} & applies all the uniformity assumptions of the above three models \\\hline\hline
time marginal & $A'=(\ones{f \times f}/f)A$ & start time independently chosen from overall distribution of start times \\\hline
size marginal & $B'=(\ones{f \times f}/f)B$ & flow size (bytes) is chosen independently of other properties \\\hline
node marginal & $S'=(\ones{f \times f}/f)S$~~~~$D'=(\ones{f \times f}/f)D$ & nodes behave distinctly, but behavior is independent of flows \\\hline
packet marginal & $Z'=(\ones{f \times f}/f)Z$~~~~$V'=(\ones{f \times f}/f)V$ & packet behavior is variable bit-rate, aggregated across all flows \\\hline
full marginal & \textit{all marginal transformations} & applies all the marginality assumptions of the above four models \\\hline\hline
source regular & $F'=(SS^t/f)F$ & flow behaviors are aggregated on a per source-node basis \\\hline
dest regular & $F'=(DD^t/f)F$ & flow behaviors are aggregated on a per destination-node basis \\\hline
mixed regular & $F'=\frac{1}{2f}(SS^t+DD^t)F$ & flow behaviors are aggregated on a mixed source/destination basis \\\hline
\end{tabular}
\caption{Matrix-based traffic models evaluated by paired differential simulation.}
\label{tab:traffic-models}
\end{center}
\vspace{-2em}
\end{table*}

@@

\begin{figure}[b]
%\vspace{-1em}
\begin{center}
\includegraphics[width=3.5in]{nodes-flows}%
\vspace{-0.75em}%
\caption{The number of active nodes and flows over time.} 
\label{fig:nodes-flows}
\end{center}
\vspace{-0.9em}
\end{figure}

@@

\break
Before using the traces, it is necessary to extract application-level behavior from the trace header data. First, we split the trace into individual packet flows. A flow is a series of packets sharing the following five attributes: \caps{IP} and transport protocols (raw \caps{IP}, \caps{ICMP}, \caps{TCP}, \caps{UDP}); source and destination \caps{IP} addresses and \caps{TCP}/\caps{UDP} port numbers. Next, the quantity of application-initiated data contained in each packet is calculated. For non-\caps{TCP} packets, this quantity is simply the size of the transport-layer payload, but for \caps{TCP} the calculation is more complicated: only new data transfers, explicitly initiated by the application are counted. Data retransmitted by \caps{TCP} is disregarded, and empty \caps{ACK}s are ignored. \caps{SYN} and \caps{FIN} flags in packets (even empty ones) are counted as a single byte each, since they are explicitly signaled by the application. %After processing, we have a collection of flows, each with a sequence of timestamps and the amount of application-initiated data sent at that time.

>>>>

\begin{table*}
\begin{center}
\small
\begin{tabular}{|c|c|l|}
\multicolumn{1}{c}{\textbf{model}} &
\multicolumn{1}{c}{\textbf{transformation}} &
\multicolumn{1}{c}{\textbf{description}} \\
\hline
{\footnotesize{GMM}} & --- & the general matrix model \\\hline\hline
time uniform & $A'=A(\ones{d_t \times d_t}/d_t)$ & all start times are equally likely \\\hline
node uniform & $S'=S(\ones{n \times n}/n)$~~~~$D'=D(\ones{n \times n}/n)$ & nodes behave stochastically identically with respect to flows \\\hline
full uniform & \textit{all uniform transformations} & applies all the uniformity assumptions of the above three models \\\hline\hline
time marginal & $A'=(\ones{f \times f}/f)A$ & start times chosen from marginal distribution of start times \\\hline
size marginal & $B'=(\ones{f \times f}/f)B$ & flow size (bytes) is chosen independently of other properties \\\hline
node marginal & $S'=(\ones{f \times f}/f)S$~~~~$D'=(\ones{f \times f}/f)D$ & nodes behave distinctly, but behavior is independent of flows \\\hline
packet marginal & $Z'=(\ones{f \times f}/f)Z$~~~~$V'=(\ones{f \times f}/f)V$ & packet behavior is variable bit-rate, aggregated across all flows \\\hline
full marginal & \textit{all marginal transformations} & applies all the marginality assumptions of the above four models \\\hline\hline
source regular & $F'=(SS^t/f)F$ & flow behaviors are aggregated on a per source-node basis \\\hline
dest regular & $F'=(DD^t/f)F$ & flow behaviors are aggregated on a per destination-node basis \\\hline
mixed regular & $F'=\frac{1}{2f}(SS^t+DD^t)F$ & flow behaviors are aggregated on a mixed source/destination basis \\\hline
\end{tabular}
\caption{Matrix-based traffic models evaluated by paired differential simulation.}
\label{tab:traffic-models}
\end{center}
\vspace{-2em}
\end{table*}

@@

\begin{figure}[t]
\vspace{0.5em}
\begin{center}
\includegraphics[width=3.3in]{nodes-flows}%
\vspace{-1.25em}%
\caption{The number of active nodes and flows over time.} 
\label{fig:nodes-flows}
\end{center}
\vspace{-2em}
\end{figure}

@@

Before using the traces, it is necessary to extract application-level behavior from the trace header data. First, we split the trace into individual packet flows. A flow is a series of packets sharing the following five attributes: \caps{IP} and transport protocols (raw \caps{IP}, \caps{ICMP}, \caps{TCP}, \caps{UDP}); source and destination \caps{IP} addresses and \caps{TCP}/\caps{UDP} port numbers. Next, the quantity of application-initiated data contained in each packet is calculated. For non-\caps{TCP} packets, this quantity is simply the size of the transport-layer payload, but for \caps{TCP} the calculation is more complicated: only new data transfers, explicitly initiated by the application are counted. Data retransmitted by \caps{TCP} is disregarded, and empty \caps{ACK}s are ignored. \caps{SYN} and \caps{FIN} flags in packets (even empty ones) are counted as a single byte each, since they are explicitly signaled by the application. %After processing, we have a collection of flows, each with a sequence of timestamps and the amount of application-initiated data sent at that time.
